---
title: "Analysis "
author: "Sara Wang"
output:
  html_document: default
  pdf_document: default
---


**Questions to ask: ** In the Coursera platform, thousands of students are taking data analysis online classes. Each of these classes includes a final project. For the *Getting and Cleaning Data project*, we want to explore the main sources of variation in how people complete the project.

**Data Source: ** [Getting and Cleaning Data project](https://github.com/search?utf8=✓&q=getting+and+cleaning+data&type=)


```{r}
# get data version 2

# sort based on dates. lubridate
library(dplyr)
library(gh)
library(lubridate)

# "Cite Andrew Leroux's code to get dates"
date_start <- ymd("2015-12-01")        ## start date
day_inc  <- 14                       ## increment days by 14 at a time
dates <- c()
i <- 1
while(date_start < Sys.Date() - (day_inc+1)) {
        dates[[i]] <- c(rep(date_start,2) %m+% c(days(-1),days(day_inc+1)))
        date_start <- date_start + days(day_inc + 1)
        i <- i + 1
}
rm(list=c("date_start","i","day_inc"))



### NOTE: Need to create a personal access authentication token for using GET /seach/code!!!
### Do this here: https://github.com/settings/tokens
token <- readLines("githubtoken.txt")
repos <- c()
#length(dates)
for (dates_num in length(dates[1:2])){

### Only 100 results per page (the max). Change page=1 parameter to get all the repositories.
gh_date <- paste("created:", paste(dates[[dates_num]], collapse=".."), sep="")

  #1:10
  for (page_num in 1:2){

    repo_name <- paste0("GET /search/repositories?q=getting+and+cleaning+data+",
            gh_date, "&per_page=100")
    x <- try(gh(repo_name, page = page_num, .token = token))
    
    if ("try-error" %in% class(x)) break
    
    repos <- c(sapply(x[[3]], "[[", "full_name"),repos)
    #print(page_num)
  }
  
  Sys.sleep(60)
}

save(repos, file = "repos.rda")
```


```{r}
load("repos.rda")
rfile_list <- list()
# "Cite Stephen's code to use gh function getting repo names"

#length(repos)
for (i in length(repos)){

  string <- paste0("GET /search/code?q=repo:", repos[[i]],"+extension:r")
  res <- try(gh::gh(string, .token=token))
  
  if ("try-error" %in% class(res)) break
  # loop_path to get all .R files
  path <- try(res[[3]][[1]]$path)
  if ("try-error" %in% class(path)) break
  
  code.url <- file.path("https://raw.githubusercontent.com",repos[[i]], "master", path)
  code.url <- gsub(" ","%20",code.url)
  code <- code.url %>% readLines(warn = FALSE)
  execode <- code[!grepl("^#", code) & !grepl("\\ ^#", code) & code != "" & code != " "]
  
  
  rfile_list[[i]] <- execode
  print(i)
  Sys.sleep(10)
}



save(rfile_list, file = "rfile_list.rda")

```
**explotary analysis: ** check how many times libraries, functions, base R are used in the repos.
```{r}

load("rfile_list.rda")
rfile_text <- unlist(rfile_list)
library_usage <- rfile_text[grep("library\\(", rfile_text)]

table(library_usage)
barplot(table(library_usage))

```






